---
title: "Solving the Maze"

output: html_document
---

This is a challenge from [Anarchy Golf](http://golf.shinh.org/p.rb?maze+solving) where the input is an ASCII maze drawn with hashes,  
```{r eval=F}
############################# ###########
#   #   #       #     #     #     #     #
# # # ### ##### ### ### ### ##### # #####
# # # #   #   #       # #   #     #     #
# # # # ### # ####### # ##### ### ### # #
# # #   #   #   # #   # #     # # #   # #
### # ### # ### # # ### # ##### # ##### #
#   #     #   #   # #   # #   # # #   # #
# ########### ##### ### # ### # # # # # #
#   #       #     # #   # #     # # # # #
# # ##### ####### # # ### # ##### # # # #
  #       #   # # #     #       #   # # #
# ########### # # ##### ####### ####### #
# #   #       #   #   #   #   #     #   #
# # # ### ####### # ##### # ##### # # ###
# # #   #     #         #       # # #   #
# ##### ### ### ####### ####### # ##### #
# #       #   #     #   #     # #   # # #
# # ##### ### ##### # ### ### # # # # # #
#       #           #     #   #   #     #
#########################################
```


and the output is the the solution to the maze, with the solution spaces filled with periods.  

```{r eval=F}
#############################.###########
#   #   #.......#     #     #.....#     #
# # # ###.#####.### ### ### #####.# #####
# # # #...#   #.......# #   #.....#     #
# # # #.### # #######.# #####.### ### # #
# # #...#...#   # #...# #.....# # #   # #
### #.###.#.### # #.### #.##### # ##### #
#   #.....#...#   #.#   #.#   # # #   # #
# ###########.#####.### #.### # # # # # #
#   #       #.....#.#   #.#     # # # # #
# # ##### #######.#.# ###.# ##### # # # #
..#       #   # #.#.....#.......#   # # #
#.########### # #.#####.#######.####### #
#.#   #       #  .#   #...#   #...  #   #
#.# # ### #######.# #####.# #####.# # ###
#.# #   #     #...      #.......#.# #   #
#.##### ### ###.####### #######.#.##### #
#.#.......#   #.....#   #     #.#.  # # #
#.#.#####.### #####.# ### ### #.#.# # # #
#...    #...........#     #   #...#     #
#########################################
```


Although the ultimate goal is to accomplish this with the shortest script possible,
it's an opportunity to look at a few different methods to tackle the problem. After all, one method 
will to be more easily shortened than the others. Here are three possible strategies.  
  
  
1. Select by Filling
    + Begin at first edge space.
    + Make "fill" function or something along those lines, which operates 
    like an image editor's bucket tool.
    + For all spaces where you have one way you can go, make 
    that choice.
    + For all spaces where you have 2 or more options, 
    close off all options but one, "fill" it, and if the 
    other edge space (victory) is filled as a result, 
    make that choice.
    + Rinse and repeat until you reach other edge space.
2. Use "Robot" with Memory
    + Record each time the robot moves.
    + For spaces where the robot has more than one place to go, 
    it chooses one and remembers which one it chose.
    + If it hits a dead end, it goes back to the last place 
    it made a choice, and makes another one.
    + If it has made all choices at a place, it backtracks to 
    the one before that etc.
3. Record All Paths
    + Use fill function again.
    + This time, each iteration of the fill procedure adds to a recorded path.
    + when there is more than one available space and the fill function splits, 
    create a new record for each option.
    + When the fill is finished, one of the recorded paths will go from one end space to the other.
    + Select that path as the solution.  
  
  
  
  
  
  This project will investigate each, and find the one best suited to be shortened and submitted.   
